### 2018-06-11 Thesis/Parts/Motivation/Motivation.tex
thesis update

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\section{Motivation}
\header{Domain specific}
Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
%start of literal quote
in-domain training of the word embeddings can drastically improve the process of document clustering. In fact, the effect is even stronger than the number of training examples and the model architecture. However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary\cite{Truong2017Thesis}. 
%end of literal quote
\citet{lai2016generate} found that 
%start literal quote
the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance. 
%end literal quote
These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.

\newpage

\header{Problems in validation}
Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}. However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly but that the available validation sets cannot confirm this.\\
Furthermore, a study by \citet{schnabel2015evaluation} found that the quality of embeddings are tasks specific, \textit{different tasks favour different embeddings}. They also found that the embeddings encode information about word frequency, even in models that are created to prevent this. \textit{This casts doubt on the common practice of using vanilla cosine similarity as a similarity measure}.\\
Therefore, we propose the validation of domain specific word-embeddings through a classification tasks, using multiple vector-distance calculations. This eliminates the need for labelled data in the validation of these domain specific word embeddings, will validate the quality of word embeddings for domain specific texts, and will validate the impact of different vector-distance measures on a categorization task.
\begin{table}
\begin{center}
\begin{tabular}{c c c c}
&WordSim & Men & RareWords\\
Lowest & 0.38 & 0.54 & 0.29 \\
Highest & 0.49 & 0.61 & 0.32\\
Average & 0.45 & 0.59 & 0.32\\
Baseline & \textbf{0.64} & \textbf{0.68} & \textbf{0.34}
\end{tabular}
\end{center}
\caption{Results for the different validation sets of word simularity validations on domain specific texts from the study by \citet{Truong2017Thesis}}\label{table:truongErrorRates}
\end{table}
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\section{Motivation}
\header{Domain specific}
Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
%start of literal quote
in-domain training of the word embeddings can  improve the process of document clustering. This effect is even stronger than the number of training examples and the model architecture.\cite{Truong2017Thesis}. 
%end of literal quote
\citet{lai2016generate} found that 
%start literal quote
the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance. 
%end literal quote
These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.

\header{Problems in validation}
To assess the quality (or usability) of the embeddings, validation methods are used. This are tasks designed to produce a metric that gives an indication of the usability of the provided embeddings. \citet{schnabel2015evaluation} found that the validation method indicates only the quality of an embedding for a specific task. There is (yet) no methtod that can asses the usability of an embedding on all possible tasks, since each task may require other information to be embedded into the embedding.
Validation methods use either labelled or unlabelled data. Labelled data is data that is in some way marked, so that the correct answer can be derived from it. Unlabelled is the opposite, this data is not marked.\\
The usage of labelled data is common practice for validation methods, since the results produced by this data can be easily checked checked.
Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}. However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly but that the available validation sets cannot confirm this.\\
Furthermore, a study by \citet{schnabel2015evaluation} found that the quality of embeddings are tasks specific, \textit{different tasks favour different embeddings}. They also found that the embeddings encode information about word frequency, even in models that are created to prevent this. \textit{This casts doubt on the common practice of using vanilla cosine similarity as a similarity measure}.\\
Therefore, we propose the validation of domain specific word-embeddings through a classification tasks, using multiple vector-distance calculations. This eliminates the need for labelled data in the validation of these domain specific word embeddings, will validate the quality of word embeddings for domain specific texts, and will validate the impact of different vector-distance measures on a categorization task.
\begin{table}
\begin{center}
\begin{tabular}{c c c c}
&WordSim & Men & RareWords\\
Best results from the research by Truong: & 0.49 & 0.61 & 0.32\\
Average  results from the research by Truong & 0.45 & 0.59 & 0.32\\
\end{tabular}
\end{center}
\caption{Results for the different validation sets of word simularity validations on domain specific texts from the study by \citet{Truong2017Thesis}}\label{table:truongErrorRates}
\end{table}
\end{document}

### 2018-06-11 Thesis/Parts/Research_setup/Research_setup.tex
thesis update

\subheader{Create embeddings}
For this research, we used word-embeddings (created using the word2vec model) and TF-IDF embeddings. The word-embeddings were created with the word2vec model from PySparks MlLib library\cite{PysparkMlLib}. The embeddings have a vector size of 300. We used Elseviers' internal, pre-made word-embeddings for this research because of the training-time required for the word2vec model.
The TF-IDF embeddings were created with the TF-IDF model from pyspark's MlLib library\cite{PysparkMlLib}, in combination with a term hasher (HashingTF) from the same library. We used multiple hashing dimensions: 100, 256, 300 \& 512. Since the TF-IDF uses the output of the term hasher, the TF-IDF model produces the same dimensions.
\subheader{Filter articles}
We create our initial set of articles by collecting all articles from the journals that were published in the year 2017, and have at least 200 publications in 2017. This reduces the journal set to $2,679$ journals, resulting in a set of $18,870,446$ articles.
\subheader{Create training and validation set}
We split our initial set in an 80\% - 20\% split, we use the 80\% set as the training set for the journal embeddings, and the 20\% set as the validation set for the journal embeddings.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings by averaging all title embeddings as the journal title embedding, and by averaging all abstract embeddings as the journal abstract embedding. We also normalized both embeddings. 
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal. To calculate the distance, we use cosine similarity (as provided by the SciPy library\cite{SciPy}). During this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subheader{Performance measurement}
We use multiple metrics to indicate the performance of the embeddings on a categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median abstract rank}
\item{Median title rank}
\end{enumerate}
\subheader{ - F1-score}
We calculate the F1 score per article, to do this, we use the following metrics:\\
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\\\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\\\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$\\
\subheader{ - Median abstract rank}
We use the median abstract rank to indicate around which rank the 'standard' article would be ranked, based on its abstract. We do this by taking the median of the abstract rank from each article.
\subheader{ - Median title rank}
We use the median title rank to indicate around which rank the 'standard' article would be ranked, based on its title. We do this by taking the median of the title rank from each article.
\end{document}

>>>>

\subheader{Create embeddings}
For this research, we used word-embeddings (created using the word2vec model) and TF-IDF embeddings. The word-embeddings were created with the word2vec model from PySparks MlLib library\cite{PysparkMlLib}. The embeddings were pre-trained and have a vector size of 300, which is an industry default. The TF-IDF embeddings were created with the TF-IDF model from pyspark's MlLib library\cite{PysparkMlLib}, in combination with a token hasher (HashingTF) from the same library. We used multiple hashing dimensions and multiple vocabulary sizes. Since the TF-IDF uses the output of the term hasher, the TF-IDF model produces the same dimensions. We will denote the tfidf sets as vocabulary size/hashing size. All of our sets, both embedding and TF-IDF, use tokenized texts.
\subsubheader{Tokenization}
== TODO ==
\subsubheader{TF-IDF selection}
To limit computational expenses, we used only the top performing which can reasonably be kept in RAM. The plot displays the ranking \& size for the 1000/1000, 4000/4000, 7000/7000 and 10.000/10.000 sets respectively.\\
\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
The plot show the median abstract \& title rank and the storage size in Gigabytes (1024 based) plotted over feature size, which is equal to the hashing size for these sets. The plot shows that both title and abstract are stagnating, while the memory usage is, slowly, going up. At a feature size of 10.000, we have a storage size of 11.6GB. Given this size and the stagnation of the rankings, we chose to use the 10.000/10.000 feature size tfidf vectors, we furthermore used the 10.000/5000 set and the 5000/5000 set for comparison.

\subsubheader{Embeddings}
We have made use of multiple embedding sets for this research. All sets share the same (default) embedding and have been (uniquely) modified. For this research we have used the following embedding sets:
\begin{enumerate}
\item{Default embedding}
\subitem{The embedding as generated by word2vec, without further enhancements.}
\item{TF-IDF embedding}
\subitem{The embedding as generated by the word2vec, multiplied by their tfidf weights to embed word priorities. We use this enhancement to give the embeddings more information about the corpus.}
\item{10K TF-IDF Embedding}
\subitem{The embedding as generated by the word2vec, filtered on the top 10.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to try to filter out possible noise created by lots of words with few occurrences.}
\item{5K TF-IDF Embedding}
\subitem{The embedding as generated by the word2vec, filtered on the top 5.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to cancel out the noise caused be rare words more aggressively}
\item{1K 6K TF-IDF Embedding}
\subitem{The embeddings as generated by the word2vec, filtered on the top top 1.000 till top 5.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to ignore the top 1.000 most common words, which are most likely generic words, since they occur often. And to cancel out the rare-words, by cutting off all words after 6K. This gives us a set of 5K words.}
\end{enumerate}

\subheader{Filter articles}
We create our initial set of articles by collecting all articles from the journals that were published in the year 2017, and have at least 200 publications in 2017. This reduces the journal set to $3,759$ thousand journals, resulting in a set of $1,391,543$ million articles ().
\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings by averaging all title embeddings as the journal title embedding, and by averaging all abstract embeddings as the journal abstract embedding. We also normalized both embeddings. 
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal. To calculate the distance, we use cosine similarity (as provided by the SciPy library\cite{SciPy}). During this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subheader{Performance measurement}
We use multiple metrics to indicate the performance of the embeddings on a categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median \& average rank}
\item{Rank distribution}
\end{enumerate}
\subsubheader{F1-score}
We define the positive \& negative metrics as follows:\\
\begin{jumpin}
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
\end{jumpin}
We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
\begin{jumpin}
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
\end{jumpin}
\subsubheader{Median \& average rank}
We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of most articles in our validation set. This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
\subsubheader{Rank distribution}
To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape. We limit ourselves to the following categories: 1 (absolute hits), top-10, top-20, top-30, top-40, top-50,  top-100 and 100+. 
\end{document}

% RAW DATA:
% 1,391,543 articles
% 14,742,192 title tokens
% 171,474,473 abstract tokens
% 3,759 journals

% split = 79.9509609117 - 20.0490390883

% training numbers
% 10K = percentage?}
